\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-10 manuscript/main.tex
modified:   manuscript/main.tex

In the Appendix Table \ref{tab:} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model

>>>>

In the Appendix Table \ref{tab:sylized_fact_hetero_hhi} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}
